---
title: 'DRAFT: G360 System Diver preliminary data'
author: "G360 - Andrew Stockford, Jonathan Kennel, Beth Parker"
date: "20/10/2020"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(transducer)
library(ggplot2)
library(data.table)
library(earthtide)
# library(waterlevel)
library(knitr)
library(xtable)
library(patchwork)
library(here)
library(plotly)
library(DT)
```


```{r read, include = FALSE, message = FALSE, warning = FALSE}

meta_path <- '/media/jonathankennel/Seagate Expansion Drive/guelph_south/meta/'
w  <- unique(fread(file.path(meta_path, 'well_details.csv')))
xd <- unique(fread(file.path(meta_path, 'transducer_details.csv')))
ma <- unique(fread(file.path(meta_path, 'manual_wl.csv')))
subs <- unique(fread(file.path(meta_path, 'transducer_subsets.csv')))
subs[, start := as.POSIXct(start, tz = 'UTC')]
subs[, end := as.POSIXct(end, tz = 'UTC')]

w[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
ma[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
xd[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']


w_elev <- unique(w[, list(well, port, elevation)])

xd <- w_elev[xd, on = c('well', 'port')]

ma <- w[ma, on = c('well', 'port')]
ma[, wl_elevation := elevation - value_manual]
ma[, datetime := as.POSIXct(datetime, tz = 'UTC')]

wn <- 'HBP-MPS1-19'


```


# Raw Summary

## Pressure

```{r summarytable, echo=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
fn <- fn[tools::file_ext(fn) == 'DAT']
y  <- read_transducer(fn)
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
nm <- xd[tools::file_ext(xd$path) == 'MON']$path
xd <- w[, list(well, port, port_depth)][xd, on = c('well', 'port'), nomatch = NA]
ma <- w[, list(well, port, port_depth)][ma, on = c('well', 'port'), nomatch = NA]
ma <- ma[well == wn]

mf <- fn[basename(fn) %in% nm]
add  <- read_transducer(mf)
add[parameter %chin% c('water_head_toc_cl', 'pressure'), channel := 'level']
add[parameter %chin% c('water_head_toc_cl', 'pressure'), parameter := 'level']
add[parameter %chin% c('level'), units := 'cmh2o']
add_p <- add[parameter == 'level']
add_t <- add[parameter == 'temperature']

add_p$data <- lapply(add_p$data, function(x) {
  x$value <- x$value * 100
  x$datetime <- x$datetime +3600*5
  x
  })
add_t$data <- lapply(add_t$data, function(x) {
  x$datetime <- x$datetime +3600*5
  x
  })

class(y[[1]]) <- 'character'
y <- rbind(y, rbind(add_p, add_t))


# y <- xd[path %in% basename(fn)]
y[, path := basename(file)]
y <- y[xd[, list(path, 
                 well, 
                 transducer_depth = depth, 
                 port, 
                 port_depth = port_depth, 
                 well_elevation = elevation, isbaro, timezone)], on = 'path', nomatch = 0]



n_digits <- 1
y_table <- y[, list(type = parameter,
                    file = basename(file),
                    # median = round(sapply(data, function(x) median(x$value)), n_digits),
                    mean = round(sapply(data, function(x) mean(x$value)), n_digits),
                    max = round(sapply(data, function(x) max(x$value)), n_digits),
                    min = round(sapply(data, function(x) min(x$value)), n_digits),
                    # sd = round(sapply(data, function(x) sd(x$value)), n_digits),
                    n = sapply(data, nrow))
]

setkey(y_table, type, file)

lev <- copy(y_table)[type=='level']
lev[, type := NULL]
knitr::kable(lev, rownames = FALSE, caption = 'Raw pressure (cm H2O)')



```

## Temperature

```{r summarytabletemp, echo=FALSE}

temp <- y_table[type=='temperature']
temp[, type := NULL]
knitr::kable(temp, rownames = FALSE, caption = 'Raw temperature (degrees C)')

```

# `r wn`


```{r pressure, echo=FALSE}

y <- y[parameter == 'level']

y <- y[well == wn]
y[, data := lapply(data, filter_dates, subsets = subs)]


y$data <- lapply(y$data, function(x) {
  x$value <- x$value / 100
  x
  })

y <- y[, data := .(.(make_even_times(data[[1]], diff_time = dt))), by = 1:nrow(y)]
y <- westbay_to_elevation(y, baro_port = 'Baro')
y <- downsample_data(y, time_interval = 300)

# y <- trim_downloads(y, n_vals = c(1800, 7200))


```

## Monitoring with Diver

Six ports and barometric pressure were monitored at `r wn`. The total monitoring period is `r min(y$start)` to  `r max(y$start)` every `r unique(y$dt)` seconds.


Pressure was output as meters $H_2O$ water level.

$z_{trans} = z_{toc} - y_{cable}$

$wl_{masl} = z_{trans} + (P_{wl} - P_{atm})$



where wl~masl~ is the equivalent water level elevation, z~toc~ is the elevation of the top of casing in m, y~cable~ is the distance from the top of casing to the transducer in m, z~trans~ is the transducer elevation in m, P~wl~ is the pressure at the port in m H~2~O, P~atm~ is the atmospheric pressure in m H~2~O. 


```{r ports, results = 'asis'}

tbl_ports <- unique(y[, list(`Port ID` = port,
                             `Transducer Depth (m)` = round(transducer_depth, 2), 
                             `Port Elevation (masl)` = round(well_elevation-port_depth, 2), 
                             `Elevation (masl)` = round(well_elevation-transducer_depth, 2), 
                             Serial = serial)])
setkey(tbl_ports, 'Port ID')
tbl_ports <- xtable(tbl_ports, caption = 'Port information.')

print(tbl_ports, include.rownames = FALSE, comment = FALSE)

```


## Hydrographs

```{r hyd1, fig.height = 8}
psia_conv = 1.0
# 1/psia_conv
# 0.4335/1/.3048


aa <- unique(rbindlist(y$data))
aa[is.na(value), wl_elevation := NA_real_]
aa[, flag := 'Submerged']
aa[value <= baro * 1.009, flag := 'In air']
# aa[flag == 'In air', wl_elevation := NA_real_]
aa[, grp := paste(as.factor(round(port_elevation, 2)))]
aa[, type := 'Water levels']
aa[is.na(port_elevation), type := 'Atmospheric']

aa[type == 'Atmospheric', wl_elevation := value / psia_conv]
setkey(aa, datetime)

ma[, grp := paste(as.factor(round(elevation - port_depth, 2)))]

xlim <- range(aa$datetime)
p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_x_datetime(limits = xlim) + 
  # scale_y_continuous(limits = c(300, 325)) +
  geom_line(na.rm = TRUE) + 
  geom_point(data = ma, aes(x = datetime, y = wl_elevation, group = grp, color = grp), na.rm = TRUE)+
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  theme_bw()

p2 <- ggplot(aa[type == 'Atmospheric'], 
             aes(x = datetime, y = value)) + 
  ylab('Atm. pressure as m H2O') + 
  scale_x_datetime(limits = xlim) + 
  geom_line(na.rm = TRUE) + 
  theme_bw()

p1 + p2 + plot_layout(widths = c(1), heights = unit(c(9.5, 3.5), c('cm', 'cm')))
```


```{r hyd2, fig.height= 8}


aa[, grp := paste('Port elevation (m):', grp)]


p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), n.breaks = 4) + 
  geom_line(na.rm = TRUE) + 
  facet_wrap(grp~., scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = "none")

print(p1)
```


## Vertical profile

```{r vert1, fig.height= 8}
daily <- aa[as.numeric(datetime) %% (86400*5) == 0]
# brks <- as.POSIXct(paste('2020', rep(1:12, each = 6), rep(c(1,5,10,15,20,25)), sep = '-'), tz = 'UTC')
brks <- seq.POSIXt(as.POSIXct('2020-01-01', tz = 'UTC'), as.POSIXct('2021-01-01', tz = 'UTC'), by = '10 days')
lbls <-as.character(brks)

ggplot(daily[type != 'Atmospheric'], 
       aes(y = wl_elevation, 
           x = port_elevation, 
           color = (datetime), 
           group = (datetime))) +
  geom_line(na.rm = TRUE) +
  ylab('Water level elevation (masl)') + 
  xlab('Port elevation (masl)') + 
  geom_point(na.rm = TRUE) +
  coord_flip() +
  scale_color_viridis_c('Day', breaks = brks, labels = lbls, expand = c(0,0)) +
  guides(color = guide_colorbar(barheight = 20)) + 
  theme_bw() 
  # guide_colorbar()

```


```{r readhbp2, include = FALSE, message = FALSE, warning = FALSE}

meta_path <- '/media/jonathankennel/Seagate Expansion Drive/guelph_south/meta/'
w  <- unique(fread(file.path(meta_path, 'well_details.csv')))
xd <- unique(fread(file.path(meta_path, 'transducer_details.csv')))
ma <- unique(fread(file.path(meta_path, 'manual_wl.csv')))
subs <- unique(fread(file.path(meta_path, 'transducer_subsets.csv')))
subs[, start := as.POSIXct(start, tz = 'UTC')]
subs[, end := as.POSIXct(end, tz = 'UTC')]

w[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
ma[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
xd[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']


w_elev <- unique(w[, list(well, port, elevation)])

xd <- w_elev[xd, on = c('well', 'port')]

ma <- w[ma, on = c('well', 'port')]
ma[, wl_elevation := elevation - value_manual]
ma[, datetime := as.POSIXct(datetime, tz = 'UTC')]

wn <- 'HBP-MPS2-19'


```


# `r wn`

```{r pressurehbp2, echo=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
fn <- fn[tools::file_ext(fn) == 'DAT']
y  <- read_transducer(fn)
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
nm <- xd[tools::file_ext(xd$path) == 'MON']$path
xd <- w[, list(well, port, port_depth)][xd, on = c('well', 'port'), nomatch = NA]
ma <- w[, list(well, port, port_depth)][ma, on = c('well', 'port'), nomatch = NA]
ma <- ma[well == wn]

mf <- fn[basename(fn) %in% nm]
add  <- read_transducer(mf)
add[parameter %chin% c('water_head_toc_cl', 'pressure'), channel := 'level']
add[parameter %chin% c('water_head_toc_cl', 'pressure'), parameter := 'level']
add[parameter %chin% c('level'), units := 'cmh2o']
add$data <- lapply(add$data, function(x) {
  x$value <- x$value * 100
  x$datetime <- x$datetime +3600*5
  x
  })
class(y[[1]]) <- 'character'
y <- rbind(y, add)


# y <- xd[path %in% basename(fn)]
y[, path := basename(file)]
y <- y[xd[, list(path, well, transducer_depth = depth, port, port_depth = port_depth, well_elevation = elevation, isbaro, timezone)], on = 'path', nomatch = 0]


y <- y[parameter == 'level']

y <- y[well == wn]
y[, data := lapply(data, filter_dates, subsets = subs)]


y$data <- lapply(y$data, function(x) {
  x$value <- x$value / 100
  x
  })

y <- y[, data := .(.(make_even_times(data[[1]], diff_time = dt))), by = 1:nrow(y)]
y <- westbay_to_elevation(y, baro_port = 'Baro')
y <- downsample_data(y, time_interval = 300)

y <- trim_downloads(y, n_vals = c(1800, 7200))


```

## Monitoring with Diver

Six ports and barometric pressure were monitored at `r wn`. The total monitoring period is `r min(y$start)` to  `r max(y$start)` every `r unique(y$dt)` seconds.


Pressure was output as meters $H_2O$ water level.

$z_{trans} = z_{toc} - y_{cable}$

$wl_{masl} = z_{trans} + (P_{wl} - P_{atm})$



where wl~masl~ is the equivalent water level elevation, z~toc~ is the elevation of the top of casing in m, y~cable~ is the distance from the top of casing to the transducer in m, z~trans~ is the transducer elevation in m, P~wl~ is the pressure at the port in m H~2~O, P~atm~ is the atmospheric pressure in m H~2~O. 


```{r portshbp2, results = 'asis'}

tbl_ports <- unique(y[, list(`Port ID` = port,
                             `Transducer Depth (m)` = round(transducer_depth, 2), 
                             `Port Elevation (masl)` = round(well_elevation-port_depth, 2), 
                             `Elevation (masl)` = round(well_elevation-transducer_depth, 2), 
                             Serial = serial)])
setkey(tbl_ports, 'Port ID')
tbl_ports <- xtable(tbl_ports, caption = 'Port information.')

print(tbl_ports, include.rownames = FALSE, comment = FALSE)

```


## Hydrographs

```{r hyd1hbp2, fig.height = 8}
psia_conv = 1.0
# 1/psia_conv
# 0.4335/1/.3048


aa <- unique(rbindlist(y$data))
aa[is.na(value), wl_elevation := NA_real_]
aa[, flag := 'Submerged']
aa[value <= baro *1.009, flag := 'In air']
# aa[flag == 'In air', wl_elevation := NA_real_]
aa[, grp := paste(as.factor(round(port_elevation, 2)))]
aa[, type := 'Water levels']
aa[is.na(port_elevation), type := 'Atmospheric']

aa[type == 'Atmospheric', wl_elevation := value / psia_conv]
setkey(aa, datetime)

ma[, grp := paste(as.factor(round(elevation - port_depth, 2)))]

xlim <- range(aa$datetime)

ma <- ma[port != 6]

p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_x_datetime(limits = xlim) + 
  # scale_y_continuous(limits = c(300, 325)) +
  geom_line(na.rm = TRUE) + 
  geom_point(data = ma, aes(x = datetime, y = wl_elevation, group = grp, color = grp), na.rm = TRUE)+
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  theme_bw()

p2 <- ggplot(aa[type == 'Atmospheric'], 
             aes(x = datetime, y = value)) + 
  ylab('Atm. pressure as m H2O') + 
  scale_x_datetime(limits = xlim) + 
  geom_line(na.rm = TRUE) + 
  theme_bw()

p1 + p2 + plot_layout(widths = c(1), heights = unit(c(9.5, 3.5), c('cm', 'cm')))
```


```{r hyd2hbp2, fig.height= 8}


aa[, grp := paste('Port elevation (m):', grp)]


p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), n.breaks = 4) + 
  geom_line(na.rm = TRUE) + 
  facet_wrap(grp~., scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = "none")

print(p1)
```


## Vertical profile

```{r verthbp2, fig.height= 8}
daily <- aa[as.numeric(datetime) %% (86400*5) == 0]
# brks <- as.POSIXct(paste('2020', rep(1:12, each = 6), rep(c(1,5,10,15,20,25)), sep = '-'), tz = 'UTC')
brks <- seq.POSIXt(as.POSIXct('2020-01-01', tz = 'UTC'), as.POSIXct('2021-01-01', tz = 'UTC'), by = '10 days')
lbls <-as.character(brks)

ggplot(daily[type != 'Atmospheric'], 
       aes(y = wl_elevation, 
           x = port_elevation, 
           color = (datetime), 
           group = (datetime))) +
  geom_line(na.rm = TRUE) +
  ylab('Water level elevation (masl)') + 
  xlab('Port elevation (masl)') + 
  geom_point(na.rm = TRUE) +
  coord_flip() +
  scale_color_viridis_c('Day', breaks = brks, labels = lbls, expand = c(0,0)) +
  guides(color = guide_colorbar(barheight = 20)) + 
  theme_bw() 
  # guide_colorbar()

```



```{r readhbp3, include = FALSE, message = FALSE, warning = FALSE}

meta_path <- '/media/jonathankennel/Seagate Expansion Drive/guelph_south/meta/'
w  <- unique(fread(file.path(meta_path, 'well_details.csv')))
xd <- unique(fread(file.path(meta_path, 'transducer_details.csv')))
ma <- unique(fread(file.path(meta_path, 'manual_wl.csv')))
subs <- unique(fread(file.path(meta_path, 'transducer_subsets.csv')))
subs[, start := as.POSIXct(start, tz = 'UTC')]
subs[, end := as.POSIXct(end, tz = 'UTC')]

w[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
ma[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
xd[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']


w_elev <- unique(w[, list(well, port, elevation)])

xd <- w_elev[xd, on = c('well', 'port')]

ma <- w[ma, on = c('well', 'port')]
ma[, wl_elevation := elevation - value_manual]
ma[, datetime := as.POSIXct(datetime, tz = 'UTC')]

wn <- 'HBP-MPS3-19'


```


# `r wn`

```{r pressurehbp3, echo=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
fn <- fn[tools::file_ext(fn) == 'DAT']
y  <- read_transducer(fn)
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
nm <- xd[tools::file_ext(xd$path) == 'MON']$path
xd <- w[, list(well, port, port_depth)][xd, on = c('well', 'port'), nomatch = NA]
ma <- w[, list(well, port, port_depth)][ma, on = c('well', 'port'), nomatch = NA]
ma <- ma[well == wn]

mf <- fn[basename(fn) %in% nm]
add  <- read_transducer(mf)
add[parameter %chin% c('water_head_toc_cl', 'pressure'), channel := 'level']
add[parameter %chin% c('water_head_toc_cl', 'pressure'), parameter := 'level']
add[parameter %chin% c('level'), units := 'cmh2o']
add$data <- lapply(add$data, function(x) {
  x$value <- x$value * 100
  x$datetime <- x$datetime +3600*5
  x
  })
class(y[[1]]) <- 'character'
y <- rbind(y, add)


# y <- xd[path %in% basename(fn)]
y[, path := basename(file)]
y <- y[xd[, list(path, well, transducer_depth = depth, port, port_depth = port_depth, well_elevation = elevation, isbaro, timezone)], on = 'path', nomatch = 0]


y <- y[parameter == 'level']

y <- y[well == wn]
y[, data := lapply(data, filter_dates, subsets = subs)]


y$data <- lapply(y$data, function(x) {
  x$value <- x$value / 100
  x
  })

y <- y[, data := .(.(make_even_times(data[[1]], diff_time = dt))), by = 1:nrow(y)]
y <- westbay_to_elevation(y, baro_port = 'Baro')
y <- downsample_data(y, time_interval = 300)

y <- trim_downloads(y, n_vals = c(1800, 7200))


```

## Monitoring with Diver

Six ports and barometric pressure were monitored at `r wn`. The total monitoring period is `r min(y$start)` to  `r max(y$start)` every `r unique(y$dt)` seconds.


Pressure was output as meters $H_2O$ water level.

$z_{trans} = z_{toc} - y_{cable}$

$wl_{masl} = z_{trans} + (P_{wl} - P_{atm})$



where wl~masl~ is the equivalent water level elevation, z~toc~ is the elevation of the top of casing in m, y~cable~ is the distance from the top of casing to the transducer in m, z~trans~ is the transducer elevation in m, P~wl~ is the pressure at the port in m H~2~O, P~atm~ is the atmospheric pressure in m H~2~O. 


```{r portshbp3, results = 'asis'}

tbl_ports <- unique(y[, list(`Port ID` = port,
                             `Transducer Depth (m)` = round(transducer_depth, 2), 
                             `Port Elevation (masl)` = round(well_elevation-port_depth, 2), 
                             `Elevation (masl)` = round(well_elevation-transducer_depth, 2), 
                             Serial = serial)])
setkey(tbl_ports, 'Port ID')
tbl_ports <- xtable(tbl_ports, caption = 'Port information.')

print(tbl_ports, include.rownames = FALSE, comment = FALSE)

```


## Hydrographs

```{r hyd1hbp3, fig.height = 8}
psia_conv = 1.0
# 1/psia_conv
# 0.4335/1/.3048


aa <- unique(rbindlist(y$data))
aa[is.na(value), wl_elevation := NA_real_]
aa[, flag := 'Submerged']
aa[value <= baro *1.009, flag := 'In air']
# aa[flag == 'In air', wl_elevation := NA_real_]
aa[, grp := paste(as.factor(round(port_elevation, 2)))]
aa[, type := 'Water levels']
aa[is.na(port_elevation), type := 'Atmospheric']

aa[type == 'Atmospheric', wl_elevation := value / psia_conv]
setkey(aa, datetime)

ma[, grp := paste(as.factor(round(elevation - port_depth, 2)))]

xlim <- range(aa$datetime)
p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_x_datetime(limits = xlim) + 
  # scale_y_continuous(limits = c(300, 325)) +
  geom_line(na.rm = TRUE) + 
  geom_point(data = ma, aes(x = datetime, y = wl_elevation, group = grp, color = grp), na.rm = TRUE)+
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  theme_bw()

p2 <- ggplot(aa[type == 'Atmospheric'], 
             aes(x = datetime, y = value)) + 
  ylab('Atm. pressure as m H2O') + 
  scale_x_datetime(limits = xlim) + 
  geom_line(na.rm = TRUE) + 
  theme_bw()

p1 + p2 + plot_layout(widths = c(1), heights = unit(c(9.5, 3.5), c('cm', 'cm')))

# aa <- rbindlist(y[port == '6']$data)
# p1 <- plot_ly(aa, x = ~datetime, y = ~wl_elevation, type = 'scatter', mode = 'lines') 
# p1

```


```{r hyd2hbp3, fig.height= 8}


aa[, grp := paste('Port elevation (m):', grp)]


p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), n.breaks = 4) + 
  geom_line(na.rm = TRUE) + 
  facet_wrap(grp~., scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = "none")

print(p1)
```


## Vertical profile

```{r verthbp3, fig.height= 8}
daily <- aa[as.numeric(datetime) %% (86400*5) == 0]
# brks <- as.POSIXct(paste('2020', rep(1:12, each = 6), rep(c(1,5,10,15,20,25)), sep = '-'), tz = 'UTC')
brks <- seq.POSIXt(as.POSIXct('2020-01-01', tz = 'UTC'), as.POSIXct('2021-01-01', tz = 'UTC'), by = '10 days')
lbls <-as.character(brks)

ggplot(daily[type != 'Atmospheric'], 
       aes(y = wl_elevation, 
           x = port_elevation, 
           color = (datetime), 
           group = (datetime))) +
  geom_line(na.rm = TRUE) +
  ylab('Water level elevation (masl)') + 
  xlab('Port elevation (masl)') + 
  geom_point(na.rm = TRUE) +
  coord_flip() +
  scale_color_viridis_c('Day', breaks = brks, labels = lbls, expand = c(0,0)) +
  guides(color = guide_colorbar(barheight = 20)) + 
  theme_bw() 
  # guide_colorbar()

```



```{r readhbp4, include = FALSE, message = FALSE, warning = FALSE}

meta_path <- '/media/jonathankennel/Seagate Expansion Drive/guelph_south/meta/'
w  <- unique(fread(file.path(meta_path, 'well_details.csv')))
xd <- unique(fread(file.path(meta_path, 'transducer_details.csv')))
ma <- unique(fread(file.path(meta_path, 'manual_wl.csv')))
subs <- unique(fread(file.path(meta_path, 'transducer_subsets.csv')))
subs[, start := as.POSIXct(start, tz = 'UTC')]
subs[, end := as.POSIXct(end, tz = 'UTC')]

w[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
ma[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
xd[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']


w_elev <- unique(w[, list(well, port, elevation)])

xd <- w_elev[xd, on = c('well', 'port')]

ma <- w[ma, on = c('well', 'port')]
ma[, wl_elevation := elevation - value_manual]
ma[, datetime := as.POSIXct(datetime, tz = 'UTC')]

wn <- 'HBP-MPS4-20'


```


# `r wn`

```{r pressurehbp4, echo=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
fn <- fn[tools::file_ext(fn) == 'DAT']
y  <- read_transducer(fn)
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
nm <- xd[tools::file_ext(xd$path) == 'MON']$path
xd <- w[, list(well, port, port_depth)][xd, on = c('well', 'port'), nomatch = NA]
ma <- w[, list(well, port, port_depth)][ma, on = c('well', 'port'), nomatch = NA]
ma <- ma[well == wn]

mf <- fn[basename(fn) %in% nm]
add  <- read_transducer(mf)
add[parameter %chin% c('water_head_toc_cl', 'pressure'), channel := 'level']
add[parameter %chin% c('water_head_toc_cl', 'pressure'), parameter := 'level']
add[parameter %chin% c('level'), units := 'cmh2o']
add$data <- lapply(add$data, function(x) {
  x$value <- x$value * 100
  x$datetime <- x$datetime +3600*5
  x
  })
class(y[[1]]) <- 'character'
y <- rbind(y, add)


# y <- xd[path %in% basename(fn)]
y[, path := basename(file)]
y <- y[xd[, list(path, well, transducer_depth = depth, port, port_depth = port_depth, well_elevation = elevation, isbaro, timezone)], on = 'path', nomatch = 0]


y <- y[parameter == 'level']

y <- y[well == wn]
y[, data := lapply(data, filter_dates, subsets = subs)]


y$data <- lapply(y$data, function(x) {
  x$value <- x$value / 100
  x
  })

y <- y[, data := .(.(make_even_times(data[[1]], diff_time = dt))), by = 1:nrow(y)]
y <- westbay_to_elevation(y, baro_port = 'Baro')
y <- downsample_data(y, time_interval = 300)

y <- trim_downloads(y, n_vals = c(1800, 7200))


```

## Monitoring with Diver

Six ports and barometric pressure were monitored at `r wn`. The total monitoring period is `r min(y$start)` to  `r max(y$start)` every `r unique(y$dt)` seconds.


Pressure was output as meters $H_2O$ water level.

$z_{trans} = z_{toc} - y_{cable}$

$wl_{masl} = z_{trans} + (P_{wl} - P_{atm})$



where wl~masl~ is the equivalent water level elevation, z~toc~ is the elevation of the top of casing in m, y~cable~ is the distance from the top of casing to the transducer in m, z~trans~ is the transducer elevation in m, P~wl~ is the pressure at the port in m H~2~O, P~atm~ is the atmospheric pressure in m H~2~O. 


```{r portshbp4, results = 'asis'}

tbl_ports <- unique(y[, list(`Port ID` = port,
                             `Transducer Depth (m)` = round(transducer_depth, 2), 
                             `Port Elevation (masl)` = round(well_elevation-port_depth, 2), 
                             `Elevation (masl)` = round(well_elevation-transducer_depth, 2), 
                             Serial = serial)])
setkey(tbl_ports, 'Port ID')
tbl_ports <- xtable(tbl_ports, caption = 'Port information.')

print(tbl_ports, include.rownames = FALSE, comment = FALSE)

```


## Hydrographs

```{r hyd1hbp4, fig.height = 8}
psia_conv = 1.0
# 1/psia_conv
# 0.4335/1/.3048


aa <- unique(rbindlist(y$data))
aa[is.na(value), wl_elevation := NA_real_]
aa[, flag := 'Submerged']
aa[value <= baro *1.009, flag := 'In air']
# aa[flag == 'In air', wl_elevation := NA_real_]
aa[, grp := paste(as.factor(round(port_elevation, 2)))]
aa[, type := 'Water levels']
aa[is.na(port_elevation), type := 'Atmospheric']

aa[type == 'Atmospheric', wl_elevation := value / psia_conv]
setkey(aa, datetime)

ma[, grp := paste(as.factor(round(elevation - port_depth, 2)))]

xlim <- range(aa$datetime)
p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_x_datetime(limits = xlim) + 
  # scale_y_continuous(limits = c(300, 325)) +
  geom_line(na.rm = TRUE) + 
  geom_point(data = ma, aes(x = datetime, y = wl_elevation, group = grp, color = grp), na.rm = TRUE)+
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  theme_bw()

p2 <- ggplot(aa[type == 'Atmospheric'], 
             aes(x = datetime, y = value)) + 
  ylab('Atm. pressure as m H2O') + 
  scale_x_datetime(limits = xlim) + 
  geom_line(na.rm = TRUE) + 
  theme_bw()

p1 + p2 + plot_layout(widths = c(1), heights = unit(c(9.5, 3.5), c('cm', 'cm')))
```


```{r hyd2hbp4, fig.height= 8}


aa[, grp := paste('Port elevation (m):', grp)]


p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), n.breaks = 4) + 
  geom_line(na.rm = TRUE) + 
  facet_wrap(grp~., scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = "none")

print(p1)
```


## Vertical profile

```{r verthbp4, fig.height= 8}
daily <- aa[as.numeric(datetime) %% (86400*5) == 0]
# brks <- as.POSIXct(paste('2020', rep(1:12, each = 6), rep(c(1,5,10,15,20,25)), sep = '-'), tz = 'UTC')
brks <- seq.POSIXt(as.POSIXct('2020-01-01', tz = 'UTC'), as.POSIXct('2021-01-01', tz = 'UTC'), by = '10 days')
lbls <-as.character(brks)

ggplot(daily[type != 'Atmospheric'], 
       aes(y = wl_elevation, 
           x = port_elevation, 
           color = (datetime), 
           group = (datetime))) +
  geom_line(na.rm = TRUE) +
  ylab('Water level elevation (masl)') + 
  xlab('Port elevation (masl)') + 
  geom_point(na.rm = TRUE) +
  coord_flip() +
  scale_color_viridis_c('Day', breaks = brks, labels = lbls, expand = c(0,0)) +
  guides(color = guide_colorbar(barheight = 20)) + 
  theme_bw() 
  # guide_colorbar()

```



```{r readgstw, include = FALSE, message = FALSE, warning = FALSE}

meta_path <- '/media/jonathankennel/Seagate Expansion Drive/guelph_south/meta/'
w  <- unique(fread(file.path(meta_path, 'well_details.csv')))
xd <- unique(fread(file.path(meta_path, 'transducer_details.csv')))
ma <- unique(fread(file.path(meta_path, 'manual_wl.csv')))
subs <- unique(fread(file.path(meta_path, 'transducer_subsets.csv')))
subs[, start := as.POSIXct(start, tz = 'UTC')]
subs[, end := as.POSIXct(end, tz = 'UTC')]

w[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
ma[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']
xd[well == 'HBP-MW3-19', well := 'HBP-MPS3-19']


w_elev <- unique(w[, list(well, port, elevation)])

xd <- w_elev[xd, on = c('well', 'port')]

ma <- w[ma, on = c('well', 'port')]
ma[, wl_elevation := elevation - value_manual]
ma[, datetime := as.POSIXct(datetime, tz = 'UTC')]

wn <- 'GSTW1-08'


```


# `r wn`

```{r pressuregstw, echo=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
fn <- fn[tools::file_ext(fn) == 'DAT']
y  <- read_transducer(fn)
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
nm <- xd[tools::file_ext(xd$path) == 'MON']$path
xd <- w[, list(well, port, port_depth)][xd, on = c('well', 'port'), nomatch = NA]
ma <- w[, list(well, port, port_depth)][ma, on = c('well', 'port'), nomatch = NA]
ma <- ma[well == wn]

mf <- fn[basename(fn) %in% nm]
add  <- read_transducer(mf)
add[parameter %chin% c('water_head_toc_cl', 'pressure'), channel := 'level']
add[parameter %chin% c('water_head_toc_cl', 'pressure'), parameter := 'level']
add[parameter %chin% c('level'), units := 'cmh2o']
add$data <- lapply(add$data, function(x) {
  x$value <- x$value * 100
  x$datetime <- x$datetime +3600*5
  x
  })
class(y[[1]]) <- 'character'
y <- rbind(y, add)


# y <- xd[path %in% basename(fn)]
y[, path := basename(file)]
y <- y[xd[, list(path, well, transducer_depth = depth, port, port_depth = port_depth, well_elevation = elevation, isbaro, timezone)], on = 'path', nomatch = 0]


y <- y[parameter == 'level']

y <- y[well == wn]
y[, data := lapply(data, filter_dates, subsets = subs)]


y$data <- lapply(y$data, function(x) {
  x$value <- x$value / 100
  x
  })

y <- y[, data := .(.(make_even_times(data[[1]], diff_time = dt))), by = 1:nrow(y)]
y <- westbay_to_elevation(y, baro_port = 'Baro')
y <- downsample_data(y, time_interval = 300)

y <- trim_downloads(y, n_vals = c(1800, 7200))


```

## Monitoring with Diver

Six ports and barometric pressure were monitored at `r wn`. The total monitoring period is `r min(y$start)` to  `r max(y$start)` every `r unique(y$dt)` seconds.


Pressure was output as meters $H_2O$ water level.

$z_{trans} = z_{toc} - y_{cable}$

$wl_{masl} = z_{trans} + (P_{wl} - P_{atm})$



where wl~masl~ is the equivalent water level elevation, z~toc~ is the elevation of the top of casing in m, y~cable~ is the distance from the top of casing to the transducer in m, z~trans~ is the transducer elevation in m, P~wl~ is the pressure at the port in m H~2~O, P~atm~ is the atmospheric pressure in m H~2~O. 


```{r portsgstw, results = 'asis'}

tbl_ports <- unique(y[, list(`Port ID` = port,
                             `Transducer Depth (m)` = round(transducer_depth, 2), 
                             `Port Elevation (masl)` = round(well_elevation-port_depth, 2), 
                             `Elevation (masl)` = round(well_elevation-transducer_depth, 2), 
                             Serial = serial)])
setkey(tbl_ports, 'Port ID')
tbl_ports <- xtable(tbl_ports, caption = 'Port information.')

print(tbl_ports, include.rownames = FALSE, comment = FALSE)

```


## Hydrographs

```{r hyd1gstw, fig.height = 8}
psia_conv = 1.0
# 1/psia_conv
# 0.4335/1/.3048


aa <- unique(rbindlist(y$data))
aa[is.na(value), wl_elevation := NA_real_]
aa[, flag := 'Submerged']
aa[value <= baro *1.009, flag := 'In air']
# aa[flag == 'In air', wl_elevation := NA_real_]
aa[, grp := paste(as.factor(round(port_elevation, 2)))]
aa[, type := 'Water levels']
aa[is.na(port_elevation), type := 'Atmospheric']

aa[type == 'Atmospheric', wl_elevation := value / psia_conv]
setkey(aa, datetime)

ma[, grp := paste(as.factor(round(elevation - port_depth, 2)))]

xlim <- range(aa$datetime)
p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_x_datetime(limits = xlim) + 
  # scale_y_continuous(limits = c(300, 325)) +
  geom_line(na.rm = TRUE) + 
  geom_point(data = ma, aes(x = datetime, y = wl_elevation, group = grp, color = grp), na.rm = TRUE)+
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  theme_bw()

p2 <- ggplot(aa[type == 'Atmospheric'], 
             aes(x = datetime, y = value)) + 
  ylab('Atm. pressure as m H2O') + 
  scale_x_datetime(limits = xlim) + 
  geom_line(na.rm = TRUE) + 
  theme_bw()

p1 + p2 + plot_layout(widths = c(1), heights = unit(c(9.5, 3.5), c('cm', 'cm')))
```


```{r hyd2gstw, fig.height= 8}


aa[, grp := paste('Port elevation (m):', grp)]


p1 <- ggplot(aa[type != 'Atmospheric'], 
             aes(x = datetime, y = wl_elevation, group = grp, color = grp)) + 
  ylab('Water level elevation (masl)') + 
  scale_color_brewer('Port Elevation', type = 'qual', palette = 'Set1') + 
  scale_y_continuous(labels = scales::number_format(accuracy = 0.01), n.breaks = 4) + 
  geom_line(na.rm = TRUE) + 
  facet_wrap(grp~., scales = 'free_y', ncol = 1) + 
  theme_bw() +
  theme(legend.position = "none")

print(p1)
```


## Vertical profile

```{r vertgstw, fig.height= 8}
daily <- aa[as.numeric(datetime) %% (86400*5) == 0]
# brks <- as.POSIXct(paste('2020', rep(1:12, each = 6), rep(c(1,5,10,15,20,25)), sep = '-'), tz = 'UTC')
brks <- seq.POSIXt(as.POSIXct('2020-01-01', tz = 'UTC'), as.POSIXct('2021-01-01', tz = 'UTC'), by = '10 days')
lbls <-as.character(brks)

ggplot(daily[type != 'Atmospheric'], 
       aes(y = wl_elevation, 
           x = port_elevation, 
           color = (datetime), 
           group = (datetime))) +
  geom_line(na.rm = TRUE) +
  ylab('Water level elevation (masl)') + 
  xlab('Port elevation (masl)') + 
  geom_point(na.rm = TRUE) +
  coord_flip() +
  scale_color_viridis_c('Day', breaks = brks, labels = lbls, expand = c(0,0)) +
  guides(color = guide_colorbar(barheight = 20)) + 
  theme_bw() 
  # guide_colorbar()

```
