---
title: "Organizing water level data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(transducer)
library(data.table)
library(readxl)
library(ggplot2)

```





## File types supported (alphabetical order):

- Diver .mon (ascii), .dat (binary)
- Levelogger .lev (ascii), .xle (xml)
- Micron .xlsx (Microsoft Excel)
- RBR .rsk (SQLite3 database)
- Westbay .csv (ascii)

If you would like an additional file type supported please let me know.



## Diver

```{r setup, include=FALSE}
fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/guelph_south', full.names = TRUE)
table(tools::file_ext(fn))

dat <- read_transducer(fn[tools::file_ext(fn) == 'MON'], n_cores = 14)

dat <- downsample_data(dat, 3600)
dat <- subset_time_interval(dat, start = as.POSIXct('2020-03-26', tz = 'UTC'))
dat <- trim_downloads(dat, n_vals = 2)
dat <- combine_files(dat)


plt <- dat[parameter != 'temperature']
plt <- plt[, rbindlist(data), by = list(serial)]

p <- ggplot(plt, aes(x = datetime, y = value))
p <- p + geom_line()
p <- p + facet_wrap(serial~., scales = 'free_y')
p <- p + theme_bw()
p

# fn <- list.files('/home/jonathankennel/Storage/data/diver/mon', full.names = TRUE)
# dat <- read_transducer(fn, n_cores = 14)

```



## Levelogger

```{r setup, include=FALSE}

fn <- list.files('/home/jonathankennel/Storage/data/levelogger/lev', full.names = TRUE)
dat <- read_transducer(fn)

# need a faster xle parser
fn <- list.files('/home/jonathankennel/Storage/data/levelogger/xle', full.names = TRUE)
dat <- read_transducer(fn, n_cores = 14)

```


## Micron

```{r setup, include=FALSE}

fn <- list.files('/home/jonathankennel/Storage/data/micron/xlsx', full.names = TRUE)
dat <- read_transducer(fn)

```




## Westbay

Currently, no support is provided for the binary .wd2 files which requires the user to output the files to a csv prior to import into R.

```{r setup, include=FALSE}

fn <- list.files('/home/jonathankennel/Storage/data/westbay/mosdax', full.names = TRUE)

dat <- read_transducer(fn, n_cores = 8)
names(dat)

```


## RBR

```{r setup, include=FALSE}


fn <- list.files('/media/jonathankennel/Seagate Expansion Drive/rbr_ssfl', full.names = TRUE)[1:8]

system.time(dat <- read_transducer(fn, n_cores = 8))


```


## Tips

- Make the raw data read only.
- Create a compressed back-up of the raw data.
- Keep all raw downloads together but separated by type.  
- Keep each raw data type separate (ie different folders for each)
  - RBR
  - Westbay
  - Diver
  - Other
- Do not mix exported data with raw download data. The exported data should be treated as disposable.
- Field notes should be in a format that is archivable with a simple structure.  The goal is to keep these files simple in structure.
- Try to be precise with time.  To the minute at least.
- Keep track of timezone information EST, EDT, PST, UTC etc. I prefer if everything is in UTC but often this is not possible. You may want to include this in the filename even.
- May want to protect the Westbay box from the elements
- Use automated naming of files.  You can add to it but do not change the autoname.
- When working in a GUI try to keep track of what you have done.  Maybe have a separate readme file.
- In general use regular time spacings
- When calibrating thing of the range you will be exposing the transducers to.

